Title

### 2015-12-09 paper/paper.tex

%\usepackage[backend=bibtex]{biblatex}
\usepackage{cite}

@@

\section{Introduction}

\section{Background}
\subsection{AMR}
\subsection{Discourse Planning}

@@

\pagebreak
\bibliographystyle{acm}
\bibliography{paper}

\end{document}

>>>>

\usepackage{cite}

@@

\section{Introduction}
\section{Background}
\subsection{Semantic Representation}

Abstract Meaning Representation (AMR)\cite{amr_sembank} attempts to unify the
semantic representation of natural language sentences. Unlike syntactic
annotations, semantic annotations often differ for different semantic relations
(named entities, temporal entities, co-referencing, etc). AMR, by contrast,
provides a single, graphical representation of the logical meaning of a
sentence, which can be easily understood by both humans and computers. For
example, % TODO: example sentence in AMR + graphical form here

An AMR-annotated sentence is directed, rooted, labeled graph, or as a
conjunction of logical triples. Throughout this paper, we work with the AMRs
exclusively in the graphical form $G=(V,E)$, and will thus refer to the AMR
using just the sets $V,E$.

\subsection{Discourse Planning}

@@

\pagebreak
\bibliographystyle{acm}
\bibliography{paper}
\end{document}
